% Written for use of the University of South Carolina, Columbia Cyber Security Club.
% This constitution is an updated version to the former constitution. This version 
% includes the "Webmaster" Officer position.
%
% Date of Last Edit: February 2nd, 2020

\documentclass[10pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{latexsym,amsfonts,amssymb,amsthm,amsmath, enumerate, hyperref}

\setlength{\parindent}{0in}
\setlength{\oddsidemargin}{0in}
\setlength{\textwidth}{6.3in}
\setlength{\textheight}{9.2in}
\setlength{\topmargin}{-0.5in}
\setlength{\headheight}{10pt}

\author{UofSC CyberSec VP, 2020}

\begin{document}
\begin{center}
\Large\textbf{Constitution of the UofSC CyberSecurity Club}
\newline
\end{center}

%========== PREAMBLE ==========
\subsection*{Preamble}
We, the students of the University of South Carolina, in order to promote the education and applicable
experience of prospective information technology professionals, particularly with regards to the topics of cyber security and
information assurance, do hereby ordain and establish this constitution.
\vspace{0.1in}
%======================= ARTICLE I ============================ 
\section*{Article I: Name}
The official title of the organization shall be the \textit{Cyber Security Club}.
\vspace{0.2in}

%======================= ARTICLE II =========================== 
\section*{Article II: Mission}
The mission of the Cyber Security Club is to raise awareness of the importance of cyber security and to
educate our members in the practice thereof. The Cyber Security Club seeks to accomplish this mission
by holding regular club meetings during which security related topics will be discussed, as well as
taking part in cyber security competitions.
\vspace{0.2in}

%====================== ARTICLE III =========================== 
\section*{Article III: Membership}
\subsection*{Section 1}
Membership in Cyber Security Club shall be limited to persons officially connected with the University
of South Carolina, Columbia as faculty, staff, or students. Students enrolled in the spring semester
under the above conditions who have pre-registered for the fall semester, as well as students enrolled in
summer classes, are eligible for summer membership.
\subsection*{Section 2}
The University of South Carolina does not discriminate in educational or employment opportunities or
decisions for qualified persons on the basis of race, color, religion, sex, national origin, age, disability,
sexual orientation or veteran status.
\subsection*{Section 3}
Membership shall be open to all University of South Carolina students and must comply with federal
laws prohibiting discrimination on the basis of race, color, sex, gender, disability, age, sexual
orientation, national or ethnic origin, political, veteran or religious affiliation/status. Compliance with
these laws means that membership, benefits, and the election of officers will not be made on the basis
of these factors. 
\subsection*{Section 4}
A person shall be considered a core member if they have paid the dues required for the year, which
shall be established in the first week of every semester of the club’s operation. General membership is 
open to anyone, regardless of whether they pay dues, but certain activities and benefits will be limited
to core members only
\subsection*{Section 5}
The organization and its members shall abide by all applicable laws of the state of South Carolina and
the United States.
\subsection*{Section 6}
The organization and its members shall abide by all applicable rules and regulations of the University
of South Carolina, and under privileges as granted by its governing bodies.
\subsection*{Section 7}
Members of this club may be exposed to information and techniques that can be used in disruptive,
unlawful, and unethical ways. Members are expected to maintain the highest ethical standards and may
be required to sign a code of ethics statement upon joining the club. Members found to be acting in an
unethical, unlawful, or deliberately disruptive manner may be expelled from the Cyber Security Club.
\vspace{0.2in}

%========================== ARTICLE IV =========================
\section*{Article IV: Officers and Terms of Office}
\subsection*{Section 1}
Any core member of Cyber Security Club can become an officer if they are elected at the annual
elections and can only hold one position at a time. Any student seeking to hold or holding office
must maintain the cumulative GPR requirement for graduation and remain in good standing
in their respective college. The officers of this organization shall be:
\begin{enumerate}[(a)]
    % ============== PRESIDENT ============== 
    \item President -- The President shall preside at all club and executive meetings. It is the responsibility of the President to conduct all meetings impartially and to protect each member’s rights. Other responsibilities of the President shall include the following duties:
    \begin{enumerate}[1.]
        \item Attending all club and executive meetings.
        \item Opening meetings at the time at which the organization is to meet.
        \item Announcing upcoming events, topics, and activities at the onset of every meeting.
        \item Stating and putting to vote all questions concerning the future of the club and its activities, and announce the result of the vote.
        \item Making executive decisions in the case of a tie vote.
        \item Other responsibilities, powers, and duties as may be assigned to their position by this constitution, by vote of the membership, or governing bodies of the University of South Carolina.
        \item Maintaining this organization in good standing with the University of South Carolina via communication with the necessary University entities.
        \item Appointing or calling for a vote for the position of team captain for any competitions that require such a position. However, the club Advisor has the right to call for replacement of any team captain found to be not suitable.
        \item Working closely with the other governing members to plan and organize club events, topics, and practice sessions.
    \end{enumerate}
    % ============ Vice President =========== 
    \item Vice President -- The Vice President, in the absence of the President, or should the President prove unable or unwilling to perform the duties described above, shall assume the responsibilities of the President. Other responsibilities of the Vice President shall include the following duties:
    \begin{enumerate}[1.]
        \item Attending all club and executive meetings.
        \item Consulting with the President on all matters and performing duties that may be assigned by the President when needed.
        \item Working closely with the other governing members to plan and organize club events, topics, and practice sessions.
        \item Organizing official recruitment events and fundraisers to reach out to the students at the University and recruit new members to the organization.
        \item Finding events such as competitions, seminars, conferences, and/or any educating or motivating event for the members of the Cyber Security Club to participate in.
    \end{enumerate}
    % ============ TREASURER ================
    \item Treasurer -- Responsibilities of the Treasurer shall include:
    \begin{enumerate}[1.]
        \item Attending all club and executive meetings.
        \item Coordinating with the vice president concerning the organization of fundraising events.
        \item Collecting dues every semester from the members of the club.
        \item Keeping a record of all club transactions and the current balance of the club funds.
        \item Coordinating with governing bodies concerning the allocation of funds for club events
    \end{enumerate}
    % ============ SECRETARY =================
    \item Secretary -- Responsibilities of the Secretary shall include: 
    \begin{enumerate}[1.]
        \item Attending all club and executive meetings.
        \item Arranging for reservation of suitable rooms and meeting places.
        \item Attending club meetings and maintaining a record of topics discussed therein.
        \item Providing to the CTO information or media to be posted to the web site when necessary
        \item Acting as a record keeper of all events in which the club participates, including filing any documentation provided at team events.
        \item Keeping a record of active members and taking attendance at every meeting.
        \item Working with the treasurer to keep a record of the core members in good standing.
        \item Coordinating with the CTO to maintain a record of all privileged account credentials for services hosted on club machines.
    \end{enumerate}
    % ============= CTO ====================
    \item Chief Technology Officer -- Responsibilities of the CTO shall include:
    \begin{enumerate}[1.]
        \item Attending all club and executive meetings.
        \item Maintaining the club servers, with responsibilities including but not limited to:
        \begin{enumerate}
            \item Maintaining images installed on the servers for club practice.
            \item Handling the restoration of services in the event of an outage.
            \item Keeping a record of machines, services, and networking information.
            \item Providing/revoking access and permissions to core members as needed.
            \item Working with the Advisor and university entities to keep the practice environment and servers safe.
        \end{enumerate}
    \end{enumerate}
    % ============ WEBMASTER =================
    \item Webmaster -- Responsibilities of the Webmaster shall include:
    \begin{enumerate}[1.]
        \item Attending all club and executive meetings.
        \item Maintaining and updating the content on the club website at \url{usccyber.org}.
        \item Handling any external club inquiries made through the website.
    \end{enumerate}
\end{enumerate}
\subsection*{Section 2}
Officers may be removed with a two-thirds (2/3) vote of the core members. The officer in question
must be notified of the vote of removal at least one (1) week in advance and shall have the opportunity
to speak before the core members prior to the vote.
\vspace{0.2in}

% ======================== ARTICLE V =============================
\section*{Article V: Advisors}
The club shall have a faculty or staff Advisor who will settle disputes amongst board members (such as,
but not limited to, election issues), offer guidance as they see fit, and attend any club events that they
wish. The Faculty/ Staff Advisor must be selected from full-time faculty or administrative staff
members at the university.\\\\
The Advisor shall work with departmental and university systems staffs to facilitate a safe practice
environment for the Cyber Security Club. The Advisor will act as the liaison for university entities in
regards to problems with or misuse of the practice environment and servers.
\vspace{0.2in}

% ======================== ARTICLE VI =============================
\section*{Article VI: Executive Board}
The Executive Board of the Cyber Security Club shall be composed of the President, Vice President,
Treasurer, Secretary, Chief Technology Officer, the Advisor, and any appointee deemed appropriate by
the President.
\vspace{0.2in}

% ======================= ARTICLE VII ==============================
\section*{Article VII: Officer Elections}
\subsection*{Section 1}
The President, Vice President, Treasurer, Secretary, and the Chief Technology Officer of the
organization shall be elected by simple majority vote by the core members. These officers may not be
appointed, except in the case of the club's first year of operation, or under circumstances where there is
a genuine need for such action, such need being determined by the Advisor.
\subsection*{Section 2}
The officer elections will be done annually every Spring semester and the newly elected officers shall
take office fifteen (15) days prior to the end of the semester.
\subsection*{Section 3}
All of the Executive Board members shall be present at the officer elections; otherwise, the election
will be postponed until another date. The President can act as the tie-breaking vote as needed. The
election can only be repeated if a majority of the core members believe that it is necessary to do so.
\subsection*{Section 4}
In the event that an officer leaves the Cyber Security Club before their term has expired, the Advisor, at
their discretion, may either determine that a replacement should be appointed or that a mid-term
election may be held.
\vspace{0.2in}

% ========================= ARTICLE VIII ===========================
\section*{Article VIII: Meetings}
\subsection*{Section 1}
Regular meetings of the Cyber Security Club shall be held every week. The day of the week for the
weekly meetings shall be decided by the President within the first two (2) weeks of each semester and
will not be changed thereafter unless 50\% of the general body find the time disagreeable.
\subsection*{Section 2}
Quorum for the weekly meetings of the Cyber Security Club shall consist of at least 30\% of the
members of the general body, and at least 1-2 members of the executive board.
\subsection*{Section 3}
The basis of learning for the organization shall be an open forum, where presentations may be given by
any member of the organization, and discussion of the topics is encouraged.
\subsection*{Section 4}
Meetings outside of the regular weekly meetings may be held for topic discussion and practice.
\subsection*{Section 5}
While regular weekly club meetings will be open for anyone to attend, special meetings or events may
be restricted to core members of the club. Participation in team competitions will be restricted to core
members.
\vspace{0.2in}

% ========================== ARTICLE IX ===========================
\section*{Article IX: Recruitment}
It shall be the duty of all governing members to take part in active recruitment of new members to the
club, and participate in advertising the club to the student body.
\vspace{0.2in}

% ========================== ARTICLE X ============================
\section*{Article X: Finances}
It shall be the responsibility of the Treasurer to maintain the finances of the club. The funds will be kept
in a secure location as decided upon by the executive board, and shall only be expended for use by the
club for its benefit.
\vspace{0.2in}

% ========================== ARTICLE XI ============================
\section*{Article XI: Constitutional Amendments}
The constitution may be altered, if an alteration is deemed necessary, by all members of the executive
board, and such alteration must be ratified by the same board by a unanimous vote before taking effect.
The proposed changes will be distributed to the core membership at least one full week prior to the
final vote for feedback, comments and discussion.

\end{document}

